A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-25 paper.tex
.eps extension in proposed-method-flow-chart
bigger figures
bigger figures cont.
All figures are pdfs now
removing comment
Corrections and results added

\usepackage[pdftex]{graphicx}
\graphicspath{{./png/}{./eps/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}

@@

\begin{abstract}
The concepts of intuitionistic membership, and intuitionistic center of
area are proposed in this work, in order to propose a novel method for
implementing an intuitionistic fuzzy inference system. The proposed
method was implemented and compared against type-1 fuzzy inference
systems and interval Type-2 fuzzy inference systems, with uncertain
means and uncertain standard deviations, by using the
Mackey-Glass time series benchmark. A genetic algorithm was used to
optimize the parameters of each of the methods being compared, and the
results show that the intuitionistic fuzzy inference system performs
better than the other methods.
\end{abstract}

@@

A derivation of logical conclusions can be performed by using premises
that are assumed to be true, and this is known as inference, in
traditional logic. The same
technique can be extended to use fuzzy premises. In this case, all the
premises hold a grade of truthiness, and a fuzzy conclusion is derived
from the process. A popular method for performing such fuzzy inferences is a
Mamdani Fuzzy Inference System (FIS) \cite{mamdani1975experiment},
where the inputs are associated with fuzzy sets, and the outputs are
fuzzy sets themselves, which can be converted to crisp numbers
(this process is usually called \textit{defuzzification}). Other types of
fuzzy inference engines exist, such as Takagi-Sugeno-Kang  (TSK)
\cite{takagi1985fuzzy} and Tsukamoto \cite{tsukamoto1979approach}.

Fuzzy sets were initially criticized because they were said to
not be able to appropriately represent uncertainty. This problem was
addressed by L. A. Zadeh in 1975 \cite{zadeh1975concept} by creating the
concept of Type-2 Fuzzy Sets (T2-FS). This extension to type-1 fuzzy sets allowed the creation of
type-2 fuzzy inference systems (T2-FIS) \cite{mendel2002type}, and those systems that used the
traditional fuzzy sets are now called Type-1 Fuzzy Inference Systems
(T1-FIS). T2-FIS have been proved to work better than T1-FIS in many
situations, often problems that involve high levels of uncertainty, such as
noisy data.

Another extension to fuzzy sets, called Intuitionistic Fuzzy Sets
(IFS), was proposed by K. T. Atanassov
\cite{atanassov1986intuitionistic}. This extension adds the concepts
of indeterminacy and non-membership to traditional fuzzy sets. In
traditional fuzzy sets, the non-membership of an element is always the
complement of the membership, but in an IFS, the non-membership can be
represented by lower values (a deeper explanation of IFS is given in
Section \ref{preliminaries}). Whenever the sum of the membership and
the non-membership is less than 1, indeterminacy emerges, which
represents the grade of uncertainty of an element of being or not
being a member of a given set, with certain grade of membership. The
concept of indeterminacy allows an expression such as ``This is
somewhat tall, although I'm not very sure about my opinion.''

The use of IFSs in a traditional FIS should enable the handling of more
uncertainty, and one could prefer an Intuitionistic FIS (IFIS) to obtain
better accuracies without sacrificing time performance, as
inferences in a T2-FIS are very time consuming compared to a
T1-FIS. This is a consequence of the complex type
reducing procedure that is involved in the defuzzification stage in a
T2-FIS \cite{mendel2001uncertain}. Several improvements to the
algorithms involved in the inference process in a T2-FIS have been proposed
to alleviate this problem, such as the Karnik-Mendel algorithm
\cite{wu2009enhanced} and shadowed sets
\cite{pedrycz1998shadowed}. Nevertheless, a T2-FIS is usually several
times slower than a T1-FIS. Because of this time performance impact,
many works that require handling more uncertainty than a T1-FIS
use a particular case of T2-FIS, the Interval T2-FIS (IT2-FIS)
\cite{mendel2006interval}, which is faster than a general T2-FIS. A Type-1
Intuitionistic FIS (T1-IFIS) should perform better than a T1-FIS in terms
of accuracy (in problems involving data with high levels of
uncertainty), and should be faster than a T2-FIS. Furthermore, IFSs
can be implemented as part of a T2-FIS, giving as a result a T2-IFIS.

@@

A goal of this work is to propose a method to design a Mamdani IFIS that is
similar in construction to the traditional Mamdani FIS. There are works
that have successfully constructed inference engines that use IFS
instead of traditional FS, but most of these works are not Mamdani
systems. Another goal is to fully integrate the concept of
non-membership into the inference process in a meaningful way,
considering how the non-membership concept should affect the process.

@@

\section{Proposed Method}
\label{proposed-method}
%(Mario)Is a Method? Extension? Implementation?
%% (A): No lo había pensado en realidad. Es que siempre le llamo
%% Proposed Method jajajaaj. Aunque creooo que sí es un método. Es un
%% método para hacer un sistema de inferencia difusa con conjuntos
%% difusos intuicionistas
The method, for now, consists on the procedures and elements
necessary to construct a basic Intuitionistic Fuzzy Inference System
(IFIS). %(Mario)Por que basic?
%% (A): Basic porque no añado que puedas poner OR en las reglas, no
%% pongo otros métodos de defuzzificación, no pongo más funciones de
%% membresía (triangulares, etc.). Explicaré eso (y)
%(Mario)Tal vez enumerarlas? cuales procedures son?
%% (A): Los procedures son los que están en el diagramita, y las
%% explico abajo. Aun así las enumero?
An implementation was completed in order to make comparisons against
classic Fuzzy Inference Systems (FISs), such as Type-1 FIS, Interval
Type-2 and General Type-2 FIS, and prove that
the design was viable and able to contribute to better results than
the classic FISs.
%(Mario)Es el proposito del diseño comparar? Creo que puedes decir mejor algo como:
%In order to assess the advantage of our proposal in terms of X
%a comparassion with  Type-1 FIS, Interval Type-2 and General Type-2 FIS,
%is presented.

@@

In many works, intuitionistic fuzzy sets (IFSs) are constructed manualy,
by interviewing experts who assign memberships and
non-memberships to each of the values of a set (such as in %to each of the members of a set?
\cite{davarzani2013novel}). This work proposes a convenient way of
creating an IFS, imitating many systems that use Gaussian
membership functions (MFs) to facilitate an expert the representation of a
fuzzy interpretation. An example of an IFS is depicted in
Figure \ref{fs-as-ifs}. This IFS represents a classic fuzzy set, as it
satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
the MF as the red line, and the non-membership
function (NMF) as the blue line. In order to contruct the NMF, one has
to rotate a normal Gaussian MF by 180˚, and this can be seen as the
complement of the fuzzy set corresponding to a Gaussian MF.
%(Mario)Al parecer lo que se está presentando es una manera automatizada de 
% hacer IFSs? Si  es así, es más facil presentarlo
%% Si se hacen automatizadamente para poder compararlo con el tipo-1 y
%% tipo-2, pero no es el objetivo del trabajo.

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{fs-as-ifs}
  \caption{Classic Fuzzy Set Represented as an Intuitionistic Fuzzy Set}
  \label{fs-as-ifs}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs}
  \caption{An Example of an Intuitionistic Fuzzy Set - Same Mean and SD}
  \label{ifs}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs-diff-mu-sd}
  \caption{An Example of an Intuitionistic Fuzzy Set - Different Mean
    and SD}
  \label{ifs-diff-mu-sd}
\end{figure}

The first step of the inference process in a classic FIS (a flow chart
for the process in an IFIS is given in Figure \ref{flow-chart}) is to
determine what grade of membership corresponds to a given input, given a set of
%(Mario)determine what particular membership function corresponds to a 
% given input, given a set of 
%% (A): Es grade of membership, perdón. De hecho hay ese error en
%% otras partes, tengo que cambiarlo.
MFs. This is straightforward in a classic FIS, as the
membership to each input is already established in the membership
fuzzy set. For an IFIS, this work proposes a method to determine a
membership given a MF and a NMF,
which is described in (\ref{imembership}), and receives the name of
$i\mu$ (intuitionistic membership). %(Mario)Creo que este podría ser
                                %el titulo
%% (A): Para poder hacer un FIS intuicionista, necesité el
%% intuitionistic membership y el intuitionistic center of area. Cómo
%% propone el título?

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{if-membership}
  \caption{Comparison of $\mu(x)$ Against $i\mu(x)$}
  \label{if-membership}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{if-membership-drastic}
  \caption{Comparison of $\mu(x)$ Against $i\mu(x)$ With More Indeterminism}
  \label{if-membership-drastic}
\end{figure}

The next step in the inference process is to perform an $\alpha$-cut % (Mario)
La del FIS? aclaralo on the associated consequents to the antecedents that are
activated by the inputs. In a classic FIS, this process is straightforward, as
the memeberships in a fuzzy set representing a consequent are ``cut'' by
following (\ref{alpha-cut}) for every element in a fuzzy set representing a
consequent. In an intuitionistic MF, one can follow the same procedure in order
to obtain the $\alpha$-cut in the MF part, but to obtain the $\alpha$-cut in
the NMF, (\ref{nmf-alpha-cut}) must be followed. In (\ref{nmf-alpha-cut}), the
counterintuitive part is that one has to find the corresponding $\nu$ for a
given $\mu_{\alpha}$. An example of an $\alpha$-cut, with $\mu_{\alpha} = 0.6$,
is depicted in Figure \ref{alpha-cut-example}.

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{alpha-cut}
  \caption{$\alpha$-cut of an Intuitionistic Fuzzy Set}
  \label{alpha-cut-example}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{ifs-union}
  \caption{Union of Three $\alpha$-cut Intuitionistic Fuzzy Sets}
  \label{ifs-union}
\end{figure}

Finally, one has to defuzzify the aggregation of the $\alpha$-cut 
consequents, in order to obtain a crisp number that represents
it. There are a number of methods that can be used to defuzzify a
% Aclara que en los tipo Mamdani %% (A): ahhhhh cierto, cierto
fuzzy set, but the most frequently found in the literature is the
Center of Area (CoA), or simply centroid. One can obtain the centroid
of a classic fuzzy set A by using (\ref{center-of-area}). For an
IFS, one can use the concept of intuitionistic membership ($i\mu$) and
extend (\ref{center-of-area}) to obtain (\ref{if-coa}). By
substituting $(\mu(x_{i}) + \nu(x_{i}))$ by $i\mu_{A}$, one arrives at
(\ref{if-coa-simplified}), which is a simplification of (\ref{if-coa}).

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=2.5in]{if-coa-vs-coa}
  \caption{Comparison of $CoA_{A_{i}}$ Against $iCoA_{A_{i}}$}
  \label{if-coa-vs-coa}
\end{figure}

@@

The purpose of the experiments in this work is to demonstrate that the
proposed method is viable for performing inference using
intuitionistic fuzzy sets instead of classic fuzzy sets, i.e., that
the concepts of intuitionistic membership ($i\mu$) and intuitionistic
center of area ($iCoA$) enable an extension to traditional fuzzy
inference systems to support indeterminacy and non-membership. To
demonstrate this claim, this work presents a series of experiments
where the proposed method is compared against Type-1 Fuzzy Inference
Systems (T1-FISs) and Interval Type-2 Fuzzy Inference Systems
(T2-FISs) with uncertain mean and uncertain standard deviation.

The initial (and ambitious) hypothesis is that a Type-1 Intuitionistic Fuzzy System (T1-IFIS)
should perform better than a T1-FIS, as it can handle both uncertainty
and indeterminacy, and it is unclear if an IFIS should perform better
than a T2-FIS. The experiments presented in this work
cannot prove this statement profoundly, as the results will only be tested for a
single situation, which is the prediction of a subset of the
Mackey-Glass time series.

@@

A total of 400 runs were performed for every FIS. The decision for
such a high number of runs was because of trial and error. Initially,
the IFIS was being tested with a subset of the Mackey-Glass time
series of 100 points for training, and 50 for testing. This decision
was made as a consequence of the high computational time required to
process the traditional sizes of the subsets. Some of the
comparisons were successful, but others, especially against the
T2-FIS, were lacking statistical data in order to obtain a decisive
conclusion. In the end, the IT2-FIS with uncertain mean and the
IT2-FIS with uncertain standard deviation required a total of 100 and
300 runs, respectively. This led to the decision of performing 400
runs for each of the comparisons for the second experiment.

@@

As the results in Section \ref{results} demonstrate, the T1-IFIS
outperforms the T1-FIS, IT2-FIS with uncertain mean, and IT2-FIS with
uncertain standard deviation. These results sustain the claim that the
intuitionistic grade of membership ($i\mu$), and the intuitionistic center
of area ($iCoA$), proposed in Section \ref{proposed-method} allows the
creation of a T1-IFIS that can perform better than a classic T1-FIS
and an IT2-FIS.

@@

Several derivative works can result from the ideas presented in this paper. For
example, the proposed T1-IFIS can be tested using several
benchmarks, other than the Mackey-Glass time series. Also, this work
should inspire the creation of Type-2 Intuitionistic Fuzzy Inference
Systems (both the interval and general types).

>>>>

\usepackage[pdftex]{graphicx}
\graphicspath{{./pdf/}}
\DeclareGraphicsExtensions{.pdf}

@@

\begin{abstract}
This work describes a method to construct type-1 intuitionistic fuzzy
inference systems. This type of systems is able to handle more uncertainty than
a type-1 fuzzy inference system and performs faster than a type-2
fuzzy inference system. The concepts of intuitionistic membership, and
intuitionistic center of area are proposed, in order to implement a
system which is similar in design than the traditional fuzzy inference
systems. The proposed method was implemented and compared against type-1 fuzzy inference
systems and interval type-2 fuzzy inference systems, with uncertain
means and uncertain standard deviations, by using the
Mackey-Glass time series benchmark. A genetic algorithm was used to
optimize the parameters of each of the methods being compared. This
optimization ensures a fair comparison between each of the methods
against the proposed method. The results show that the intuitionistic
fuzzy inference system performs better than the other methods.
\end{abstract}

@@

The use of intuitionistic fuzzy sets (IFSs) in a traditional fuzzy
inference system (FIS) should enable the handling of more
uncertainty, and one could prefer an intuitionistic FIS (IFIS) to obtain
better accuracies without sacrificing time performance, as
inferences in a type-2 FIS (T2-FIS) are very time consuming compared to a
type-1 FIS (T1-FIS). This is a consequence of the complex type
reducing procedure that is involved in the defuzzification stage in a
T2-FIS \cite{mendel2001uncertain}. Several improvements to the
algorithms involved in the inference process in a T2-FIS have been proposed
to alleviate this problem, such as the Karnik-Mendel algorithm
\cite{wu2009enhanced} and shadowed sets
\cite{pedrycz1998shadowed}. Nevertheless, a T2-FIS is usually several
times slower than a T1-FIS. Because of this time performance impact,
many works that require handling more uncertainty than a T1-FIS
use a particular case of T2-FIS, the interval T2-FIS (IT2-FIS)
\cite{mendel2006interval}, which is faster than a general T2-FIS (GT2-FIS). A type-1
IFIS (T1-IFIS) should perform better than a T1-FIS in terms
of accuracy (in problems involving data with high levels of
uncertainty), and should be faster than a T2-FIS. Furthermore, IFSs
can be implemented as part of a T2-FIS, giving as a result a type-2 IFIS.

@@

A derivation of logical conclusions can be performed by using premises
that are assumed to be true, and this is known as inference in
traditional logic. The same technique can be extended to use fuzzy
premises. In this case, all the
premises hold a grade of truthiness, and a fuzzy conclusion is derived
from the process. A popular method for performing such fuzzy inferences is a
Mamdani FIS (FIS) \cite{mamdani1975experiment},
where the inputs are associated with fuzzy sets, and the outputs are
fuzzy sets themselves, which can be converted to crisp numbers
(this process is usually called \textit{defuzzification}). Other types of
fuzzy inference engines exist, such as Takagi-Sugeno-Kang  (TSK)
\cite{takagi1985fuzzy} and Tsukamoto \cite{tsukamoto1979approach}.

Fuzzy sets were initially criticized because they were said to
not be able to appropriately represent uncertainty. This problem was
addressed by L. A. Zadeh in 1975 \cite{zadeh1975concept} by creating the
concept of type-2 fuzzy sets (T2-FS). This extension to type-1 fuzzy sets allowed the creation of
T2-FISs \cite{mendel2002type}, and those systems that used the
traditional fuzzy sets are now called type-1 fuzzy inference systems
(T1-FIS). T2-FISs have been proved to work better than T1-FIS in many
situations, often problems that involve high levels of uncertainty, such as
noisy data \cite{mendel2001uncertain}.

Another extension to fuzzy sets, called intuitionistic fuzzy sets, was
proposed by K. T. Atanassov \cite{atanassov1986intuitionistic}. This
extension adds the concepts of indeterminacy and non-membership to
traditional fuzzy sets. In traditional fuzzy sets, the non-membership
of an element is always the
complement of the membership, but in an IFS, the non-membership can be
represented by lower values (a deeper explanation of IFS is given in
Section \ref{preliminaries}). Whenever the sum of the membership and
the non-membership is less than 1, indeterminacy emerges, which
represents the grade of uncertainty of an element of being or not
being a member of a given set, with certain grade of membership. The
concept of indeterminacy allows an expression such as ``This is
somewhat tall, although I'm not very sure about my opinion'' to be
represented in a FIS.

The goal of this work is to propose a Mamdani IFIS that is
similar in construction to the traditional Mamdani FIS. There are works
that have successfully constructed inference engines that use IFS
instead of traditional FS, but most of these works are not Mamdani
systems. Another goal is to fully integrate the concept of
non-membership into the inference process in a meaningful way,
considering how the non-membership concept should affect the process.

@@

\section{Proposed Method}
\label{proposed-method}
%(Mario)Is a Method? Extension? Implementation?
%% (A): No lo había pensado en realidad. Es que siempre le llamo
%% Proposed Method jajajaaj. Aunque creooo que sí es un método. Es un
%% método para hacer un sistema de inferencia difusa con conjuntos
%% difusos intuicionistas
The method, for now, consists on the procedures and elements
necessary to construct a basic IFIS, as this system can only handle
Gaussian membership functions, and simple rules without AND or OR operators.
An implementation was completed in order to make comparisons against
traditional FISs, such as T1-FISs, IT2-FISs, and GT2-FIS, and prove that
the design was viable and able to contribute to better results than
the traditional FISs.
%(Mario)Es el proposito del diseño comparar? Creo que puedes decir mejor algo como:
%In order to assess the advantage of our proposal in terms of X
%a comparassion with  Type-1 FIS, Interval Type-2 and General Type-2 FIS,
%is presented.

@@

In many works, IFSs are constructed manually,
by interviewing experts who assign memberships and
non-memberships to each of the elements of a set (such as in %to each of the members of a set?
\cite{davarzani2013novel}). This work proposes a convenient way of
creating an IFS, imitating many systems that use Gaussian
membership functions (MFs) to facilitate an expert the representation of a
fuzzy interpretation. An example of an IFS is depicted in
Figure \ref{fs-as-ifs}. This IFS represents a traditional fuzzy set, as it
satisfies (\ref{ifs-form}) and (\ref{fs-as-ifs-if}), by representing
the MF as the red line, and the non-membership
function (NMF) as the blue line. In order to contruct the NMF, one has
to rotate a normal Gaussian MF by 180˚, and this can be seen as the
complement of the fuzzy set corresponding to a Gaussian MF.
%(Mario)Al parecer lo que se está presentando es una manera automatizada de 
% hacer IFSs? Si  es así, es más facil presentarlo
%% Si se hacen automatizadamente para poder compararlo con el tipo-1 y
%% tipo-2, pero no es el objetivo del trabajo.

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.0in]{fs-as-ifs}
  \caption{Traditional Fuzzy Set Represented as an Intuitionistic Fuzzy Set}
  \label{fs-as-ifs}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.0in]{ifs}
  \caption{An Example of an Intuitionistic Fuzzy Set - Same Mean and SD}
  \label{ifs}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.0in]{ifs-diff-mu-sd}
  \caption{An Example of an Intuitionistic Fuzzy Set - Different Mean
    and SD}
  \label{ifs-diff-mu-sd}
\end{figure}

The first step of the inference process in a traditional FIS (a flow chart
for the process in an IFIS is given in Figure \ref{flow-chart}) is to
determine what grade of membership corresponds to a given input, given a set of
%(Mario)determine what particular membership function corresponds to a 
% given input, given a set of 
%% (A): Es grade of membership, perdón. De hecho hay ese error en
%% otras partes, tengo que cambiarlo.
MFs. This is straightforward in a traditional FIS, as the
membership to each input is already established in the membership
fuzzy set. For an IFIS, this work proposes a method to determine a
membership given a MF and a NMF,
which is described in (\ref{imembership}), and receives the name of
intuitionistic membership and is represented as $i\mu$. %(Mario)Creo que este podría ser
                                %el titulo
%% (A): Para poder hacer un FIS intuicionista, necesité el
%% intuitionistic membership y el intuitionistic center of area. Cómo
%% propone el título?

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.0in]{if-membership}
  \caption{Comparison of $\mu(x)$ Against $i\mu(x)$}
  \label{if-membership}
\end{figure}

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.0in]{if-membership-drastic}
  \caption{Comparison of $\mu(x)$ Against $i\mu(x)$ With More Indeterminism}
  \label{if-membership-drastic}
\end{figure}

The next step in the inference process of a FIS is to perform an $\alpha$-cut % (Mario) La del FIS? aclaralo
on the associated consequents to the antecedents that are
activated by the inputs. In a traditional FIS, this process is straightforward, as
the memeberships in a fuzzy set representing a consequent are ``cut'' by
following (\ref{alpha-cut}) for every element in a fuzzy set representing a
consequent. In an intuitionistic MF, one can follow the same procedure in order
to obtain the $\alpha$-cut in the MF part, but to obtain the $\alpha$-cut in
the NMF, (\ref{nmf-alpha-cut}) must be followed. In (\ref{nmf-alpha-cut}), the
counterintuitive part is that one has to find the corresponding $\nu$ for a
given $\mu_{\alpha}$. An example of an $\alpha$-cut, with $\mu_{\alpha} = 0.6$,
is depicted in Figure \ref{alpha-cut-example}.

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.0in]{alpha-cut}
  \caption{$\alpha$-cut of an Intuitionistic Fuzzy Set}
  \label{alpha-cut-example}
\end{figure}

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.0in]{ifs-union}
  \caption{Union of Three $\alpha$-cut Intuitionistic Fuzzy Sets}
  \label{ifs-union}
\end{figure}

Finally, one has to defuzzify the aggregation of the $\alpha$-cut 
consequents, in order to obtain a crisp number that represents
it. There are a number of methods that can be used to defuzzify a
% Aclara que en los tipo Mamdani %% (A): ahhhhh cierto, cierto
fuzzy set in a Mamdani FIS, but the most frequently found in the literature is the
center of area (CoA) or centroid. One can obtain the centroid
of a traditional fuzzy set A by using (\ref{center-of-area}). For an
IFS, one can use the concept of intuitionistic membership ($i\mu$) and
extend (\ref{center-of-area}) to obtain (\ref{if-coa}). By
substituting $(\mu(x_{i}) + \nu(x_{i}))$ by $i\mu_{A}$, one arrives at
(\ref{if-coa-simplified}), which is a simplification of (\ref{if-coa}).

@@

\begin{figure}[!t]
  \centering
  \includegraphics[width=3.0in]{if-coa-vs-coa}
  \caption{Comparison of $CoA_{A_{i}}$ Against $iCoA_{A_{i}}$}
  \label{if-coa-vs-coa}
\end{figure}

@@

The purpose of the experiments in this work is to demonstrate that the
proposed method is viable for performing inference using
intuitionistic fuzzy sets instead of traditional fuzzy sets, i.e., that
the concepts of intuitionistic membership ($i\mu$) and intuitionistic
center of area ($iCoA$) enable an extension to traditional fuzzy
inference systems to support indeterminacy and non-membership. To
demonstrate this claim, this work presents a series of experiments
where the proposed method is compared against T1-FISs and IT2-FISs
with uncertain mean and uncertain standard deviation.

The initial (and ambitious) hypothesis is that a T1-IFIS
should perform better than a T1-FIS, as it can handle both uncertainty
and indeterminacy, and it is unclear if an IFIS should perform better
than a T2-FIS. The experiments presented in this work
cannot prove this statement profoundly, as the results will only be tested for a
single situation, which is the prediction of a subset of the
Mackey-Glass time series.

@@

A total of 400 runs were performed for every FIS. The decision for
that particular number of runs was because of trial and error. Initially,
the IFIS was being tested with a subset of the Mackey-Glass time
series of 100 points for training, and 50 for testing. This decision
was made as a consequence of the high computational time required to
process the traditional sizes of the subsets. Some of the
comparisons were successful, but others, especially against the
T2-FIS, were lacking statistical data in order to obtain a decisive
conclusion. In the end, the IT2-FIS with uncertain mean and the
IT2-FIS with uncertain standard deviation required a total of 100 and
300 runs, respectively. This led to the decision of performing 400
runs for each of the comparisons for the second experiment.

@@

As the results in Section \ref{results} demonstrate, the T1-IFIS
outperforms the T1-FIS, IT2-FIS with uncertain mean, and IT2-FIS with
uncertain standard deviation. These results sustain the claim that the
intuitionistic grade of membership ($i\mu$), and the intuitionistic center
of area ($iCoA$), proposed in Section \ref{proposed-method} allows the
creation of a T1-IFIS that can perform better than a traditional T1-FIS
and an IT2-FIS.

@@

Several derivative works can result from the ideas presented in this paper. For
example, the proposed T1-IFIS can be tested using several
benchmarks, other than the Mackey-Glass time series. Also, this work
should inspire the creation of T2-IFIS (both the interval and general types).
